---
title: "Exporing Social Media Data"
output: html_document
---

```{r setup, include=FALSE}
# loading scripts
source("scripts/summary_info.R")
source("scripts/table.R")
source("scripts/opinion_charts.R")
source("scripts/effectiveness_charts.R")
source("scripts/opinion_by_econ.R")

library("knitr")
```
In an effort to understand the effects social media has on users, we have
decided to explore social media and how marketing tactics affect spending on
popular social media sites as well as it's over all reception by users. This
is important as it better informs users of strategies used by sites to lure
users into spending as well as allowing for the marketers themselves too see
how effectively they are marketing on certain platforms to different
demographics of consumers. In this project we have successfully found data on
[data.world](https://data.world/). The datasets we chose from data.world was
collected via survey on an app known as "Whatsgoodly". 

## Data Summary 
``` {r summary info, echo = FALSE}
info <- get_summary_info(ds)
info_influencer <- get_summary_info(data)
```
The first dataset we used included `r info$length` different columns that
addressed different pieces of information about each individual surveyed.
There were a total of `r info$total_participant` of people who responded to the
survey. The survey asked the following question: `r info$type_of_questions`
Respondents had the following answers: `r info$type_of_answer`. The survey also
categorized users into different demographics such as
`r info$type_of_participant`, and other groupings allowing us to extrapolate
different trends based on these demographics. 

The second dataset we have analyzed has `r info_influencer$length` different
columns with a total of `r info_influencer$total_participant` survey
participants. This survey inquired the following:
`r info_influencer$type_of_questions` The individuals surveyed responded to
these inquiries along with demographic information exactly the same as the
dataset above such as `r info$type_of_participant`. 

## Gender and Spending habits
The following table allows us to gain insight on spending habits by gender. The
table shows the count and percentage of each gender that found each social
media platform most influential to their shopping experiences. Based on this
information, those who wish to find trends and ideas for items based on their
gender identity can refer to those popular social media sites. Gender based
grouping can also be used in a marketing perspective as marketers are most
likely to advertise heavily on sites that have the most influence on certain
genders based on the products they sell. This allows us, to then question and
inquire further about how advertisers change their tactics based on such
demographic information and also wonder why certain groups prefer certain
social media platforms. 

Based on the table below, many interesting data points are revealed. In female
voters, Instagram seems to be a leading influence while the largest portion of
male voters voted that no social media platforms had an influence on their
shopping. This shows that women may be more susceptible to advertisements on
social media and thus may see far more targeted ads towards them. The table
also shows that out of the social medias, instagram had the highest influence
in both women and men showing that instagram is a source that wields the most
control over shopping and thus shapes trends and habits. 

``` {r table, echo = FALSE}
get_table(ds)
```

## Opinions on Social Media Marketing

As mentioned above, one of the questions asked in the Whatsgoodly surveys was
"What do you think when an influencer is obviously selling a product?". We
categorized the answers so that their responses were categorized as positive,
negative, or neutral. This allowed us to make observations on how different
demographics felt about social media marketing.

We started by looking at the overall opinion of social media marketing. Below
is a pie chart that shows this distribution according to the surveys.

``` {r all opinion, echo = FALSE}
opinion_all
```

We thought that a pie chart was an effective way of visualizing the
distribution because we found that there was a distinct enough difference in
count between the three groups. This was assisted by the easily readable
percentages within the sections. As seen in the chart, most people that took
the survey had a negative or neutral opinion on social media marketing, with
almost half of the survey takers having a negative reaction to ads.

We took a deeper dive into the question and looked at how different economic
classes felt about social media marketing.

``` {r econ opinion, echo = FALSE}
chart_econ
```

We thought that a stacked bar chart was an effective way of visualizing the
opinion counts because there was an easy way to show the amount of people in
each category. Although there were significantly differing amounts of
respondents in each category, the percentages in each economic class stay
roughly the same. They are also very similar to the overal percentages shown in
the previous pie chart.

## Effectiveness

To effectively understand how social media marketing affects user interaction,
we knew we had to figure out which platforms had the most effective ads. The
pie chart below shows the distribution of answers to the Whatsgoodly survey
question on which platform has influenced their online shopping. 

``` {r all platform, echo = FALSE}
platform_all
```

Since there was only one variable to account for, we thought that a pie chart
was effective at showing the percentages. We chose to keep the "None" category
in the bar chart because this section represents the users that are not
influenced by social media marketing. 40% of respondents responded with "None",
indicating that there was a significant amount of people who weren't affected
by the ads. Of those who were influenced by social media ads, Instagram users
were the most affected with 31% and Facebook in second with 20.4%. Note that
Instagram is owned by Facebook, which might be the reason why they account for
the greatest influence in this survey.

