---
title: "Exporing Social Media Data"
output: html_document
---

```{r setup, include=FALSE}
# loading scripts
source("scripts/summary_info.R")
source("scripts/table.R")
source("scripts/opinion_charts.R")
source("scripts/effectiveness_charts.R")

library("knitr")
```
In an effort to understand the effects social media has on users, we have decided to explore social media and how marketing tactics affect spending on popular social media sites as well as it's over all reception by users. This is important as it better informs users of strategies used by sites to lure users into spending as well as allowing for the marketers themselves too see how effectively they are marketing on certain platforms to different demographics of consumers. In this project we have successfully found data on [data.world](https://data.world/). The datasets we chose from data.world was collected via survey on an app known as "Whatsgoodly". 

## Data Summary 
``` {r summary info, echo = FALSE}
info <-get_summary_info(ds)
info_influencer <- get_summary_info(data)
```
The first dataset we used included `r info$length` different columns that addressed different pieces of information about each individual surveyed. There were a total of `r info$total_participant` of people who responded to the survey. The survey asked the following question: `r info$type_of_questions` Respondents had the following answers: `r info$type_of_answer`. The survey also categorized users into different demographics such as `r info$type_of_participant`, and other groupings allowing us to extrapolate different trends based on these demographics. 

The second dataset we have analyzed has `r info_influencer$length` different columns with a total of `r info_influencer$total_participant` survey participants. This survey inquired the following; `r info_influencer$type_of_questions` The individuals surveyed responded to these inquiries along with demographic information exactly the same as the dataset above such as `r info$type_of_participant`. 

## Gender and Spending habits
The following table allows us to gain insight on spending habits by gender. Based on this information, those who wish to find trends and ideas for items based on their gender identity can refer to those popular social media sites. Gender based grouping can also be used in a marketing perspective as marketers are most likely to advertise heavily on sites that have the most influence on certain genders based on the products they sell. This allows us, to then question and inquire further about how advertisers change their tactics based on such demographic information and also wonder why certain groups prefer certain social media platforms. 

Based on the table below, many interesting data points are revealed. In female voters, Instagram seems to be a leading influence while the largest portion of male voters voted that no social media platforms had an influence on their shopping. This shows that women may be more susceptible to advertisements on social media and thus may see far more targeted ads towards them. The table also shows that out of the social medias, instagram had the highest influence in both women and men showing that instagram is a source that wields the most control over shopping and thus shapes trends and habits. 

``` {r table, echo = FALSE}
get_table(ds)
```

``` {r opinion charts, echo = FALSE}

opinion_all
chart_econ

```
